---
title: "Homework #2 DACSS690"
author: "Annabel Smith"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "GitHub", icon: "fa-github", href: "https://github.com/DACSS690D-SpatialAnalysis/Homework2", align: right }
---


```{r setup, include=FALSE}
library(flexdashboard) # always
library(ggplot2)
```

<!-- links -->
```{r}
map1link=
viz1=url("https://github.com/DACSS690D-SpatialAnalysis/Homework2/raw/refs/heads/main/lowell_map.rds")

```

## Intro {.sidebar}

In Lowell, Massachusetts, there are 48 schools and 14 gas stations. Considering the city's size and number of gas stations, it should be reasonable that no gas station is within 150 meters of any school. 

Using geographic information about the location of both gas stations and schools in Lowell, MA, the graph to the right pinpoints three gas station locations that would be required to move following the 150 meters guideline set above. The stations determined to need relocation are marked in purple and four possible relocation sites are marked with red crosses. 

## Column {data-width="450"}

### Locations of Gas Stations and Schools in Lowell, MA <!-- a title for plot -->

```{r}

readRDS(viz1)
```


